Open Science, Open Plant Pathology

### 2020-04-20 analysis/paper/paper.Rmd
Add more references

> "The replication of scientific findings using independent investigators, methods, data, equipment, and protocols has long been, and will continue to be, the standard by which scientific claims are evaluated. However, in many fields of study there are examples of scientific investigations that cannot be fully replicated because of a lack of time or resources. In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing. One candidate for this minimum standard is ``reproducible research'', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses". Peng, R. [-@Peng2009]. Reproducible research and _Biostatistics_. Biostatistics, 10 (3): 405-408.

@@

Open science has become highlighted lately with many donors expecting data to be available (XXXX) and other scientists interested in sharing and collaborating more widely (XXXX).

>>>>

> "The replication of scientific findings using independent investigators, methods, data, equipment, and protocols has long been, and will continue to be, the standard by which scientific claims are evaluated. However, in many fields of study there are examples of scientific investigations that cannot be fully replicated because of a lack of time or resources. In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing. One candidate for this minimum standard is ``reproducible research'', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses". Peng, R. [-@Peng2009]. _Reproducible research and Biostatistics_. Biostatistics, 10 (3): 405-408.

@@

Open science has become highlighted lately with many donors expecting data to be available [@vannoorden2017; @ARC2018] and other scientists interested in sharing and collaborating more widely [@Wald2010].
